Insertion Sort Analysis in Java

### 2015-02-04 Programming Project A/Insertion Sort Analysis in Java.tex
added references, but for some reason they are not working.... :-0
got bib working
minor update
added abstract

\raggedbottom
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Remarks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Edit the used packages and their options (see above).
% 2. If you want, add a BibTeX-File to the project
%    (e.g., 'literature.bib').
% 3. Happy TeXing!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%% BEGIN ABSTRACT
\begin{abstract}
%% TODO: Write abstract
%% END ABSTRACT
\end{abstract}

%% BEGIN MOTIVATION
\section{Motivation}
In order to show how an algorithm might run on a given set of hardware, and how the algorithm will perform when given large amounts of data, algorithms are analysed. More specifically, insertion sort is analysed to determined what the run time might be for sorting large amounts of data on any modern computer.
%% END MOTIVATION

@@

%% BEGIN CONCLUSION
\section{Conclusions}
Insertion sort is not the best choice for sorting large amounts of data because as n grows large, it takes insertion sort $ \theta(n^2) $ time to complete on modern day computers. Obviously, the faster the system executing insertion sort, the faster the algorithm will complete, however, with large enough values of n, it can take powerful systems quite a long amount of time to complete, as shown in Figure 1.

%% TODO: Add more here

%% END CONCLUSION

@@

%% BEGIN REFERENCES
\section*{References}

%% TODO: Cite shit

>>>>

\raggedbottom
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Remarks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Note:
% 1. Edit the used packages and their options (see above).
% 2. If you want, add a BibTeX-File to the project
%    (e.g., 'literature.bib').
% 3. Happy TeXing!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%% BEGIN ABSTRACT
\begin{abstract}
The present study investigates the insertion sort sorting algorithm and how it performs on data sets of different sizes when implemented in Java. Insertion sort is a sorting algorithm that runs in $ \theta(n^2) $. For sorting large sets of data, insertion sort does not perform exemplary, however, for simple sorting of data sets under 10,000, insertion sort performs reasonably quickly on modern day computers. 
%% END ABSTRACT
\end{abstract}

%% BEGIN MOTIVATION
\section{Motivation}
In order to show how an algorithm might run on a given set of hardware, and how the algorithm will perform when given large amounts of data, algorithms are analysed. More specifically, insertion sort is analysed to determine what the run time might be for sorting large amounts of data on any modern computer.
%% END MOTIVATION

@@

%% BEGIN CONCLUSION
\section{Conclusions}
Insertion sort is not the best choice for sorting large amounts of data because as n grows large, it takes insertion sort $ \theta(n^2) $ time to complete on modern day computers. Obviously, the faster the system executing insertion sort, the faster the algorithm will complete, however, with large enough values of n, it can take powerful systems quite a long amount of time to complete, as shown in Figure 1. 
%% END CONCLUSION

@@

%% BEGIN REFERENCES
%%\section*{References}

\nocite{*}
\bibliographystyle{IEEEtran}
\bibliography{bib}
